The problem and promise of scale in multilayer networks

### 2020-02-03 paper/manuscript.Rmd
reflow
move header-includes affiliation to date

---
title: The problem and promise of scale in multilayer networks
author: Alec L. Robitaille^1^, Quinn M.R. Webber^2^, Julie W. Turner^1^, Eric Vander Wal^1,2^
header-includes: ^1^Department of Biology, Memorial University of Newfoundland, Canada; ^2^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland
output: 
    # bookdown::word_document2:
      # reference_docx: template.docx
    github_document
bibliography: ../references/knitcite.bib
---

>>>>

---
title: The problem and promise of scale in multilayer networks
author: Alec L. Robitaille^1^, Quinn M.R. Webber^2^, Julie W. Turner^1^, Eric Vander Wal^1,2^
date: ^1^Department of Biology, Memorial University of Newfoundland, Canada; ^2^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland
output:
  # bookdown::markdown_document2:
  #   base_format: rmarkdown::pdf_document
  # bookdown::pdf_document2
  bookdown::word_document2:
    reference_docx: template.docx
bibliography: ../references/knitcite.bib
---
